---
title: 'Tidy Tuesday #2'
author: "Put your name here"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(tidyverse)     # for graphing and data cleaning
library(lubridate)     # for date manipulation
library(ggthemes)      # for even more plotting themes
library(janitor)       # for cleaning variable names
library(knitr)
theme_set(theme_minimal()) # My favorite ggplot() theme :)
```

## Data choice 1: 

```{r}
# Read in the data for the week
airmen <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-08/airmen.csv')


# If the code above gives an error, uncomment the code below and use it instead. 
# You will need to install the tidytuesdayR package first.

# library(tidytuesdayR)
# 
# tuesdata <- tidytuesdayR::tt_load('2022-02-08')
# tuesdata <- tidytuesdayR::tt_load(2022, week = 6)

# airmen <- tuesdata$airmen
```

The first choice for this week's data is about Tuskegee Airmen. Read more about it, including definitions of variables, [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-02-08/readme.md). 

I thought I would figure out where the highest ranking of the Tuskeege Airmen came from.

```{r}
  airmen_rank <- airmen %>%
    drop_na(rank_at_graduation) %>% 
      filter(rank_at_graduation != "N/A", rank_at_graduation != "Unk") %>% 
        group_by(state, rank_at_graduation) %>% 
          mutate(rank_total = n())
```

In the above code I sort out the airmen data as to find out how many soldiers reached each rank.

```{r, fig.width = 20, fig.height = 8, fig.alt = "Graph showing distribution of soldiers' ranks organized by their home states"}
  airmen_rank %>%  
      ggplot(aes(x = state, y = rank_at_graduation)) +
      geom_tile(aes(fill = rank_total)) +
      scale_fill_gradientn(colors = c("darkblue", "blue", "green", "red")) +
      labs(title = "Rank distribution of Tuskegee Airmen by home state",
           x = "State",
           y = "",
           caption = "Number of soldiers to achieve a given rank are given by the color of tiles.",
           fill = "") +
           theme(plot.caption = element_text(size = 15))

```
It is interesting to note that while the Tuskegee institute was located in Alabama, there doesn't seem to be an extraordinary representation from the state- We also see a large number of 2nd Leiutenants from Illinios, even more so than NY or California. It does appear to be a relatively uniform spread among the states other than these few standout exceptions.

